Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-13 providence/sections/workload.tex
.

\subsection{Real time}
Given tight certification deadlines\footnote{Virginia recently passed legislation requiring pre-certification RLAs.}, the total real time to conduct the RLA is also an important factor to consider when planning audits.
Because each county can sample ballots for the same round concurrently, the total real time for a round depends only on the slowest county. 
In Virginia, Fairfax County typically has the most votes cast by a significant difference; in the contest we consider, Fairfax County had ~551 thousand votes cast, more than double the ~203 thousand of second-highest Virginia Beach City.
Consequently, we model the expected total real time $T$ of an audit using just the largest county, and we define analagous variables for the expected values in just the largest county.
For the largest county, let the expected total ballots sampled be $\bar E_b$, the expected number of rounds $\bar E_r$, and the expected number of distinct precinct samples summed over all rounds be $\bar E_p$.
Similarly, we use real time per-ballot, per-round, and per-precinct workload variables, $t_b$, $t_r$, and $t_p$. So the real time of the audit is estimated by
\begin{equation}
T(\bar E_b, \bar E_r, \bar E_p ) = \bar E_b t_b + \bar E_r t_r + \bar E_p t_p + C
\label{eq:real_time}
\end{equation}

@@

Imagine that Alice beats Bob in an election contest both truly and in the reported results, but Bob's supporters are insistent he really won. When election officials carry out the RLA, they choose a small first round size in the hopes of achieving an efficient audit by getting to stop sooner (and drawing fewer ballots on average). After the first round, by chance, there are more votes for Bob than for Alice in the sample. Bob's supporters celebrate their victory that the audit has in fact revealed that Bob really won, but the election officials have to explain that they are moving on to a second round. After the second round, there are more votes in the sample for Alice and sufficiently many that the risk limit is met and the audit now ends confirming the announced result that Alice won. This is an undesirable situation, as it can appear to Alice's supporters that election officials are simply drawing ballots till a chosen outcome is obtained.

>>>>

\subsection{Real time}
Given tight certification deadlines\footnote{Virginia recently passed legislation requiring pre-certification RLAs.}, the total real time to conduct the RLA is also an important factor to consider when planning audits.
Because each county can sample ballots for the same round concurrently, the total real time for a round depends only on the slowest county. 
In Virginia, Fairfax County typically has the most votes cast by a significant difference; in the contest we consider, Fairfax County had ~551 thousand votes cast, more than double the ~203 thousand of second-highest Virginia Beach City.
Consequently, we model the expected total real time $T$ of an audit using just the largest county, and we define analagous variables for the expected values in just the largest county.
Note that some other county may be slower, having fewer votes but also less auditing resources; but still, a slowest county exists. In this example, we take it to be Fairfax, the largest.
For the slowest county, let the expected total ballots sampled be $\bar E_b$, the expected number of rounds $\bar E_r$, and the expected number of distinct precinct samples summed over all rounds be $\bar E_p$.
Similarly, we use real time per-ballot, per-round, and per-precinct workload variables, $t_b$, $t_r$, and $t_p$. So the real time of the audit is estimated by
\begin{equation}
T(\bar E_b, \bar E_r, \bar E_p ) = \bar E_b t_b + \bar E_r t_r + \bar E_p t_p + C
\label{eq:real_time}
\end{equation}

@@

Imagine that Alice beats Bob in an election contest both truly and in the reported results, but Bob's supporters are insistent he really won. When election officials carry out the RLA, they choose a small first round size in the hopes of achieving an efficient audit by getting to stop sooner (and drawing fewer ballots on average). After the first round, by chance, there are more votes for Bob than for Alice in the sample. Bob's supporters celebrate their victory that the audit has in fact revealed that Bob really won, but the election officials have to explain that they are moving on to a second round. After the second round, there are more votes in the sample for Alice and sufficiently many that the risk limit is met and the audit now ends confirming the announced result that Alice won. This is an undesirable situation, as it can appear to Bob's supporters that election officials are simply drawing ballots till a chosen outcome is obtained.
